\documentclass{Report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{arabtex}
\title{Poetry}
\author{Suhrit}
\date{2021}
\begin{document}
\maketitle
\chapter*{April}
\section*{ }
This poem has been heavily inspired by one of the short stories of the fictional character Klaus Poppe in the manga and anime series `Monster'. I should also add that this poem has nothing to do with my beliefs on anythig to do with God.
\\
\\God sat by his beautiful fountain,
\\Right in front of the most beautiful mountain
\\
\\"I am the greatest!" He though, "I am all might!"
\\"My reflection should be an interesting sight!"
\\
\\Saying so, God walked to the fountain,
\\Closed is eyes and counted till ten.
\\
\\He opened his eyes when he was done,
\\For, he hoped that he will have some fun.
\\
\\But in front of him, behind the water,
\\A devil stood, overwhelmed with laughter.
\\
\\`I am you,' it spoke, `and you are me.'
\\`We are incomplete without the other.'
\\But God was not convinced, of course,
\\for he was, to all of creation, the ultimate Father.
\\
\\God spoke, `Your statement goes against the universe's laws.
\\It, thus, obviously full of flaws.
\\I am the saviour and you are the knife!
\\You are death and I am life!
\\I am joy when you are sorrow.
\\When you are the phantom I am the dove,
\\When you are hatred I am love.'
\\
\\The devil spoke: `The result of all life is death,
\\You have created both, and yet you side with the dove?!
\\Is it your 'Saviouship' that results in so much suffering?
\\The womb of hatred is within the hearts that love.'
\\
\\God was then left speechless,
\\For the devil had created a big mess.
\\The devil was, again, overwhelmed with laughter,
\\For even God had not known that \textit{He} was the monster.
\end{document}