\documentclass{article}
\title{Resilience}
\author{Poetic Heart}
\begin{document}
\maketitle
The wind wails and mourns even three years later;
\\For the day a monster killer her own daughter.
\\The leaves and flowers fall to on the earth,
\\For nothing remails of that poor child.
\\
\\I was called to decorate pumpkins, but I deserted them.
\\Sugar does not remain sweet, lime is not sour;
\\Only if this was some story or folklore.
\\Peace does not appeal to me, nor does disturbance.
\\
\\My will to live does not remain, nor the strength to strike my wrist.
\\My cold heart has left my head in mist.
\\Never have I worn spectacles but there is only darkness in sight.
\\Nothing has been left to see after that night.
\\
\\When I was 17, I was told to remain quiet, bear with the loss of my mother.
\\I was not able to act even when my 17 year old daughter was stabbed.
\\I could sit to curse my paralysed limbs but it is my crime to have deserted my wheelchair. 
\\
\\For my sister, who stopped my suicide,
\\For the one who gave me resilience;
\\Even thouhgh I wish to enter silence,
\\I will, till death calls either of us, wait by her side. 
\\
\\I do not have the will to live life,
\\Nor the strength to lift a knife.
\\I do not want the joys of heaven. I cannot care less about the pain of hell.
\\Since that night my chest has remained but a shell.
\\
\\She saved me when my husband died, a year ago;
\\Now how can I act just for my own ego? 
\\This rotten life must be lived on for her,
\\When nothing remains but the stone heart of a monster.
\\
\\I have no hope, nor will ever find any;
\\To kill myself and to live, both, reasons are many.
\\But for that one angel, I shall not depart;
\\For the one who set me and sorrow apart.
\\
\\The first verse of the bible, I fail to remember;
\\Visit the church, I have never.
\\Now, I sit and hope my daughter is enjoying the chill breeze and beautiful flowers heaven,
\\An apostate pleads to you, O Father, her fate now under your fist. Amen.
\end{document}